---
title: "Handling Export from Windows Familias?"
author: "Thore"
date: "1 7 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The files referred to below are in
<https://github.com/thoree/exclusion/tree/master/example-sister-mother/fam>.

The file `Familias-general-DNA-data.txt` is exported from
the `General DNA data` of Familias. It gives allele designations and
frequencies, but not more, and so mutation models etc are not there.

The file `Familias-case-data.txt` is exported from the `Case DNA data`
of Familias. It gives name and sex of individuals and 
possible genotypes.

It's also possible to export the Familias project and then
mutation models, parameters and pedigrees will also be included. 
Here's an example of loading a project exported from
Windows Familias and how it's converted to ped-suite format.

```{r, echo = TRUE, eval = TRUE}
source("Familias.R") # Loads exported from Familias.fam, kinship2 plots
library(forrel)
# Convert to ped-suite format
x = Familias2ped(pedigrees, datamatrix, loci)
# The pedigrees
(claim = x[[1]])
(true = x[[2]])
plotPedList(list(claim, true))

# Marker - and genotype data
x[[2]]$markerdata 
# or
x[[1]][[1]]$markerdata
# x[[1]] is a list of two singletons and a pedigree
# and so the following does not work
x[[1]]$markerdata
```