---
title: 'Project: exclusionPower'
author: "Thore, Elias and Magnus"
date: "`r Sys.setlocale('LC_TIME','C'); paste('Created: ', format(Sys.Date(), '%b %d, %Y'))`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Missing Grandchild Example

Below is an example based
on the Argentina paper, see Figure 6, Kling et al (2017),
https://github.com/thoree/exclusion/blob/master/F21/Kling-missing-PIIS1872497317301758.pdf.
The pedigrees are larger than usual, parents of PO typically not available,
and mutations happen.
Files are in in https://github.com/thoree/exclusion/tree/master/F21.
The data has been exported from Windows Familias
and converted using `forrel::Familias2ped`. Then it was
saved using the R function `save`. Below it's loaded (I unsuccesfuly tried several 
ways of direct load from github) and some examples
are shown based on the 5 markers published

```{r, echo = TRUE, eval = TRUE}
load("exampleA3.RData")
x = exampleA3
library(forrel, quietly = TRUE)
claim = x[[1]][[1]] # remove singleton, just for first plot
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
plot(claim, marker = 1:2, cex = 0.8,  skip.empty.genotypes = TRUE,
     shaded = 1:5, col = list(red = "POI"),
     title = "Fig 6, H1, Argentina- paper, Kling et al., 2017")
```

Exclusion probability for first marker:

```{r, echo = TRUE, eval = TRUE}
claim = x[[1]]
true = x[[2]]
(PE = exclusionPower(claim, true, ids = "POI", markerindex = 1, 
               verbose = FALSE))
```

Let's check the answer with some acrobatics, since
`oneMarkerDistribution`does not accept lists:

```{r, echo = TRUE, eval = TRUE}
library(pedprobr)
H2 = x[[2]][[1]]
H2 = addChildren(H2, father = 2, mother = "POI", id = "NN", 
                 verbose = FALSE)
ptrue = oneMarkerDistribution(H2,ids = "POI", partialmarker = 1,
                              verbose = F)

H1 = x[[1]][[1]]
pclaim = oneMarkerDistribution(H1,ids = "POI", partialmarker = 1,
                              verbose = F)
I1 = (pclaim == 0)
PE.check = sum(I1*ptrue)
c("PE = ", PE, "PE.check =", PE.check)
```




A closer look at the second marker: We see that there must be a mutation in `5`
and mutations are modelled only for this marker. In this case, `the `proportional`
model with mutation rate 0.005, was specified in Windows Familias.
In the ped-suite, we can look at the mutation model (output omitted)

```{r, echo = TRUE, eval = FALSE}
library(pedmut)
m = claim$markerdata[[2]]
mutmod(m)
```

Exclusion probability for second marker
(problem with `markerindex` see https://github.com/magnusdv/forrel/issues/23; skip the rest for now)

```{r, echo = TRUE, eval = TRUE}
exclusionPower(claim, true, ids = "POI", markerindex = 2, 
               verbose = FALSE)
```


Exclusion probability for markers 1,2,3,4,5

```{r, echo = TRUE, eval = TRUE}
nMarkers = 5
PE = rep(NA, nMarkers)
for (i in 1:5)
  PE[i] = exclusionPower(claim, true, ids = "POI", markerindex = i, plot = FALSE,
                         verbose = FALSE)
PE.all = 1 - prod(1-PE)
c("PE = " = PE.all)
```



